Safe and Robust Formal Synthesis of Digital Controllers for Continuous Plants

### 2018-03-13 automatica/paper.tex
revised sec 2

\textbf{CEGIS -}
Program synthesis is the problem of computing correct-by-design programs
from high-level specifications. Algorithms for this problem have made
substantial progress in recent years, for instance~\cite{itzhaky2010simple} 
to inductively synthesize invariants for the generation of desired programs.

>>>>

\textbf{CEGIS -} Program synthesis is the problem of computing
correct-by-design programs from high-level specifications. Algorithms
for this problem have made substantial progress in recent years, in
particular CEGIS, which is a recent approach to inductive synthesis
borrowing ideas from Counter-Example Guided Abstraction Refinement
(CEGAR)~\cite{DBLP:conf/cav/ClarkeGJLV00} and
superoptimisation~\cite{DBLP:conf/iclp/BrainCVF06,
  DBLP:conf/asplos/Massalin87}.  This approach uses an iterative
process where each iteration performs inductive generalisation based
on counterexamples provided by a verification oracle.  In the absence
of complete specifications, oracles are queried to distinguish between
non-equivalent
programs~\cite{jha-icse10,DBLP:conf/fmcad/AlurBJMRSSSTU13}.

%% for instance~\cite{itzhaky2010simple} 
%% to inductively synthesize invariants for the generation of desired programs.
